---
title: "SBM"
author: "YujiaChen"
date: "2024-11-20"
output: html_document
---

```{r library, echo=TRUE}
# Install necessary packages
install.packages(c("tidyverse", "car", "ggplot2", "lmtest", "PerformanceAnalytics"))
# Load the libraries
library(tidyverse)
library(car)
library(ggplot2)
library(lmtest)
library(PerformanceAnalytics)
library(ggplot2)

```

# Load the Data
1. **Dataset Description**
- Provide a description of the dataset(s).
- Highlight that we will analyze patents, trademarks, and CB rank for FinTech companies.
- Mention the data sources.

The dataset contains information about FinTech companies. The dataset includes the following columns:

```{r cars}
# Specify the file path
file_path <- "D:/JADS/MasterS1/SBM/Group_Assignment/Data/Crunchbase/Fintech/FinTechCompanies.csv"

# Load the CSV file
data <- read.csv(file_path)

# Check the structure of the dataset
View(data)

```

# Pick the related key variables
2. **Key Variables for H3**:

- Independent Variables (Predictors):
  - Patent Count: Total number of patents a company holds.
  - Trademark Count: Total number of trademarks registered by the company.

- Dependent Variable (Outcome):
  - CB Rank: A numerical ranking of a company’s visibility and importance on Crunchbase.

- Control Variables (to reduce bias):
  - Company Size (e.g., number of employees, revenue).
  - Age of the Company (e.g., years since founding).
  - Industry Type (categorical variable to account for differences in industry dynamics).
```{r library, echo=TRUE}

library(dplyr)

```


```{r colnames clean, echo=TRUE}
library(stringr)

colnames(data) <- str_trim(colnames(data))

colnames(data)


```

## Select the key variables for analysis:
  - CB Rank: Organization's rank on Crunchbase.
  - Patents Granted: Number of patents granted to the organization.
  - Trademarks Registered: Number of trademarks registered by the organization.
  - Number of Employees: Total number of employees in the organization.
  - Estimated Revenue Range: Estimated revenue range of the organization.
  - Age: Age of the organization.
  - Industries: Industry category of the organization.
```{r Key variables, echo=FALSE}

# Select relevant columns using exact names
selected_data <- data %>%
  select(
    `CB.Rank..Organization.`, 
    `IPqwery...Patents.Granted`, 
    `IPqwery...Trademarks.Registered`, 
    `Number.of.Employees`, 
    `Estimated.Revenue.Range`, 
    `Age`, 
    `Industries`
  ) 

# Check the  data
View(selected_data)

```

```{r}
# Check the structure of the selected data
str(selected_data)

```
```{r}
summary(selected_data)

```

# Data Cleaning and Transformation

As we can see from the output of str() , many of the fields are recognized as type character but may actually need to be converted to a more appropriate type, they Should be converted to numeric type for subsequent analysis.

1. **Data transformation**:
- Convert relevant columns to numeric type for analysis.
```{r}
selected_data$IPqwery...Patents.Granted <- as.numeric(selected_data$IPqwery...Patents.Granted)
selected_data$IPqwery...Trademarks.Registered <- as.numeric(selected_data$IPqwery...Trademarks.Registered)
selected_data$Age <- as.numeric(selected_data$Age)

```
```{r}
# Encode Number.of.Employees as a factor
selected_data$Number.of.Employees <- factor(selected_data$Number.of.Employees, 
                                            levels = c("Nov-50", "51-100", "101-250", "251-500", "501-1000", 
                                                       "1001-5000", "5001-10000", "10001+"),
                                            ordered = TRUE) 

# Encode Estimated.Revenue.Range as a factor
selected_data$Estimated.Revenue.Range <- factor(selected_data$Estimated.Revenue.Range,
                                                levels = c("Less than $1M", "$1M to $10M", "$10M to $50M", 
                                                           "$50M to $100M", "$100M to $500M", "$500M to $1B", 
                                                           "$1B to $10B", "More than $10B"),
                                                ordered = TRUE) 

```

```{r}
# Check the structure of the transformed data
# View the structure and levels of factors
levels(selected_data$Number.of.Employees)
levels(selected_data$Estimated.Revenue.Range)

# Check the overall data structure
str(selected_data)

```
```{r}
# Convert the factor to a numeric type, representing the level
selected_data$Number.of.Employees.Numeric <- as.numeric(selected_data$Number.of.Employees)
selected_data$Estimated.Revenue.Range.Numeric <- as.numeric(selected_data$Estimated.Revenue.Range)

head(selected_data)

```


2.Data cleaning:

## Handle NA Values

**Check for missing values**

```{r}
# Check for missing values

summary(selected_data)

```
**Check the proportion of missing values**

```{r}

missing_percentage <- colSums(is.na(selected_data)) / nrow(selected_data) * 100
print(missing_percentage)

```
1). IPqwery...Patents.Granted and IPqwery...Trademarks.Registered

Missing values can be reasonably assumed to be 0, because if a company does not have these data records, it usually means that they do not have patents or trademarks.

**Fill all missing values with 0**

```{r}
# Replace NA values with 0

selected_data$IPqwery...Patents.Granted[is.na(selected_data$IPqwery...Patents.Granted)] <- 0
selected_data$IPqwery...Trademarks.Registered[is.na(selected_data$IPqwery...Trademarks.Registered)] <- 0

```

2) . Number.of.Employees and Estimated.Revenue.Range
The processing of these two fields is slightly more complicated because they have important business significance for company size and revenue, and directly deleting or filling them may cause errors.

Preserve missing value information for regression models

Introduce missing value flag variables (dummy variables) to indicate whether there are missing values. This allows the model to understand the possible impact of some companies not having data records on these fields.
Processing method:

Create two new variables, such as Employees_NA and Revenue_NA, with values of 1 for missing and 0 for non-missing;
Fill the missing values of the original fields with the median or mean.

```{r}

# Create missing value flag variable
selected_data$Employees_NA <- ifelse(is.na(selected_data$Number.of.Employees), 1, 0)
selected_data$Revenue_NA <- ifelse(is.na(selected_data$Estimated.Revenue.Range), 1, 0)
```

```{r}
# Fill the original field with the median
# Create a new dataset and transform Number.of.Employees and Estimated.Revenue.Range
new_data <- selected_data %>%
  mutate(
    # Convert Number.of.Employees to an intermediate value
    Number.of.Employees.Numeric = case_when(
      Number.of.Employees == "Nov-50" ~ 25,
      Number.of.Employees == "51-100" ~ 75,
      Number.of.Employees == "101-250" ~ 175,
      Number.of.Employees == "251-500" ~ 375,
      Number.of.Employees == "501-1000" ~ 750,
      Number.of.Employees == "1001-5000" ~ 3000,
      Number.of.Employees == "5001-10000" ~ 7500,
      Number.of.Employees == "10001+" ~ 10001,
      TRUE ~ NA_real_ 
    ),
    # Convert Estimated.Revenue.Range to intermediate values
    Estimated.Revenue.Range.Numeric = case_when(
      Estimated.Revenue.Range == "Less than $1M" ~ 0.5,
      Estimated.Revenue.Range == "$1M to $10M" ~ 5,
      Estimated.Revenue.Range == "$10M to $50M" ~ 30,
      Estimated.Revenue.Range == "$50M to $100M" ~ 75,
      Estimated.Revenue.Range == "$100M to $500M" ~ 300,
      Estimated.Revenue.Range == "$500M to $1B" ~ 750,
      Estimated.Revenue.Range == "$1B to $10B" ~ 5000,
      Estimated.Revenue.Range == "More than $10B" ~ 10000,
      TRUE ~ NA_real_ # Unmatched values are set to NA
    )
  )

# Fill missing values of Number.of.Employees.Numeric
new_data$Number.of.Employees.Numeric[is.na(new_data$Number.of.Employees.Numeric)] <- 
  median(new_data$Number.of.Employees.Numeric, na.rm = TRUE)


new_data$Estimated.Revenue.Range.Numeric[is.na(new_data$Estimated.Revenue.Range.Numeric)] <- 
  median(new_data$Estimated.Revenue.Range.Numeric, na.rm = TRUE)

```

```{r}
View(new_data)
```

```{r}
summary(new_data)
```


# Visualize Variables to get some insight
- Visualize the distribution of variables to understand the data better.
- Explore relationships between variables to identify potential patterns or correlations.

```{r}
str(new_data)  
```

## A. Distributions for Variables

1. Histograms: View the distribution of each numerical variable.
```{r}

# Histogram: View the distribution of each numerical variable

ggplot(new_data, aes(x = IPqwery...Patents.Granted)) +
  geom_histogram(bins = 30, fill = "orange", alpha = 0.7) +
  labs(title = "Distribution of Patents Granted", x = "Number of Patents", y = "Frequency") +
  theme_minimal()

ggplot(new_data, aes(x = IPqwery...Trademarks.Registered)) +
  geom_histogram(bins = 30, fill = "green", alpha = 0.7) +
  labs(title = "Distribution of Trademarks Registered", x = "Number of Trademarks", y = "Frequency") +
  theme_minimal()

```
Output:
The distribution of patents granted (Figure 1) and trademarks registered (Figure 2) exhibits a highly skewed pattern. The majority of companies hold no or very few patents and trademarks, while a small subset of companies demonstrates significantly higher numbers (e.g., 200+). This indicates a long-tail distribution, where intellectual property (IP) resources are concentrated in a few firms.

The high proportion of zero values suggests that many companies in the dataset may not prioritize IP investment. However, companies with substantial IP resources might have a significant advantage, aligning with the hypothesis that greater IP investment correlates with higher CB Rank.

To address the skewed distribution and ensure robust regression analysis, log transformation or standardization of these variables is recommended. Further scatterplots and correlation analysis will help confirm the relationship between IP investments and market rank.


2. Visualization of ordered factor variables (Ord.factor)

```{r}

ggplot(new_data, aes(x = Number.of.Employees)) +
  geom_bar(fill = "purple", alpha = 0.7) +
  labs(title = "Distribution of Employee Ranges", x = "Employee Ranges", y = "Count") +
  theme_minimal()

ggplot(new_data, aes(x = Estimated.Revenue.Range)) +
  geom_bar(fill = "cyan", alpha = 0.7) +
  labs(title = "Distribution of Revenue Ranges", x = "Revenue Ranges", y = "Count") +
  theme_minimal()
```

Output:
The distribution of employee ranges (Figure 1) reveals that the majority of companies have fewer than 50 employees, indicating that the dataset predominantly represents smaller companies. Similarly, the distribution of revenue ranges (Figure 2) shows that most companies generate less than $10M annually, with few high-revenue firms. Both variables exhibit a long-tail distribution.

The large proportion of missing values (NA) in both variables warrants careful handling to ensure data integrity. Imputation or removal of missing values is recommended to avoid skewing the regression results.

These findings suggest a potential bias toward smaller and lower-revenue firms in the dataset. This skewness and the high concentration of values in the lower ranges may influence the relationship between these variables and company rankings (CB Rank). Appropriate transformations or group-level analyses are suggested to improve the robustness of the regression model.


3. Visualization of categorical variables (character)
For the categorical variable Industries, its distribution can be displayed through a bar chart or word cloud

```{r}
# Bar chart: Shows the frequency of each Industry
ggplot(new_data, aes(x = Industries)) +
  geom_bar(fill = "darkblue", alpha = 0.7) +
  labs(title = "Distribution of Industries", x = "Industry", y = "Count") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

```
There are too many values for the industry variable, so only the first 10 can be displayed by sorting by frequency.

```{r}
# Filter the top 10 industries by frequency
top_industries <- as.data.frame(table(new_data$Industries)) %>%
  arrange(desc(Freq)) %>%
  head(10)

ggplot(top_industries, aes(x = reorder(Var1, -Freq), y = Freq)) +
  geom_bar(stat = "identity", fill = "darkblue", alpha = 0.7) +
  labs(title = "Top 10 Industries", x = "Industry", y = "Count") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```
output:
The initial visualization of industry distribution (Figure 1) revealed a high level of complexity due to the large number of industry categories. To improve interpretability, we focused on the top 10 most frequent industries (Figure 2).

The results indicate that the dataset is heavily dominated by financial technology (FinTech) and related sectors, such as financial services, payments, and banking. The top industry category, "Financial Services, FinTech," accounts for nearly 1,000 observations, highlighting its prominence in the dataset. Other high-frequency industries include "Finance, Financial Services, FinTech" and "FinTech," further confirming the dominance of financial technology companies.

These findings suggest a strong concentration of companies in the FinTech space, which should be considered in subsequent regression analyses. Incorporating industry categories as dummy variables in the model may reveal their impact on the target variable, CB Rank. Additional exploration of industry-specific characteristics, such as employee size and revenue, is recommended to better understand the drivers behind industry performance.


4. Relationships Between Variables
Scatterplots can show relationships between numeric variables, such as CB Rank and Patents/Trademarks.
```{r}

# CB Rank vs. Patents Granted
ggplot(new_data, aes(x = IPqwery...Patents.Granted, y = as.numeric(CB.Rank..Organization.))) +
  geom_point(alpha = 0.5, color = "orange") +
  labs(title = "CB Rank vs Patents Granted", x = "Number of Patents", y = "CB Rank") +
  theme_minimal()

# CB Rank vs. Trademarks Registered
ggplot(new_data, aes(x = IPqwery...Trademarks.Registered, y = as.numeric(CB.Rank..Organization.))) +
  geom_point(alpha = 0.5, color = "pink") +
  labs(title = "CB Rank vs Trademarks Registered", x = "Number of Trademarks", y = "CB Rank") +
  theme_minimal()


```
Output:
Figures 1 and 2 illustrate the relationship between CB Rank and two key intellectual property indicators: patents granted and trademarks registered. Both plots show highly skewed distributions, with the majority of companies having very few or no patents and trademarks. Notably, companies with high CB Rank (lower numerical values) tend to cluster around low patent and trademark counts, indicating that the quantity of patents or trademarks alone does not directly correlate with rank.

A small number of outliers, representing companies with exceptionally high patent or trademark counts, may have contributed to their higher CB Rank, but their influence on the overall trend is limited. These findings suggest that intellectual property measures might be significant factors for ranking only under specific conditions, warranting further exploration in regression analysis.

To enhance model performance, it is recommended to preprocess these variables (e.g., log transformation) and investigate potential non-linear or interaction effects with other predictors. Additional analyses, such as correlation matrices, can provide insights into the relationships between variables and guide feature selection for regression modeling.


5. Check the correlation between numerical variables
Calculate the correlation coefficient matrix and draw a heat map to check the correlation between variables.
```{r}
library(ggcorrplot)
```


```{r}
# Calculate the correlation
numeric_vars <- new_data %>% select(IPqwery...Patents.Granted, IPqwery...Trademarks.Registered, 
                                    Number.of.Employees.Numeric, Estimated.Revenue.Range.Numeric)
cor_matrix <- cor(numeric_vars, use = "complete.obs")


ggcorrplot(cor_matrix, lab = TRUE, title = "Correlation Matrix")

```
output:
The correlation matrix highlights notable relationships among key numerical variables in the dataset. Patents granted and trademarks registered show a moderate positive correlation (0.40), reflecting a shared focus on intellectual property investments by certain companies. Estimated revenue and the number of employees also exhibit a moderate positive correlation (0.37), suggesting a potential trend where larger companies with more employees generate higher revenues.

However, other relationships, such as between patents and revenue (0.21) or patents and employees (0.17), are weaker, indicating that patents might not directly impact these metrics or are influenced by other factors. The overall low correlations suggest that these variables are relatively independent, which minimizes multicollinearity concerns for regression modeling.

These insights provide a strong foundation for further analysis, particularly exploring the role of intellectual property in company performance and its interaction with other predictors. The correlation matrix can guide variable selection and transformation strategies to enhance the regression model's predictive power and interpretability.


# Data Processing for regression analysis

To start processing and preparing `regression_data` for regression analysis, we need to complete the following steps:

1. Filter the required columns
We will only keep the required columns:

- `CB.Rank..Organization.` as the dependent variable
- `IPqwery...Patents.Granted`
- `IPqwery...Trademarks.Registered`
- `Age`
- `Industries`
- `Number.of.Employees.Numeric`
- `Estimated.Revenue.Range.Numeric`

2. Convert `CB.Rank..Organization.` variable to numeric
This column is of character type and needs to be converted to numeric type.

3. Log transform columns with highly skewed distribution
We will perform `log1p` transformation on the following columns:
- `IPqwery...Patents.Granted`
- `IPqwery...Trademarks.Registered`

4. Process the `Industries` column
`Industries` is a character type, and the following two methods can be used:
- **One-hot encoding**: Convert different industries to dummy variable columns.
- **Label encoding**: Give integer labels to industry categories.

```{r}

library(tidyverse)

```


```{r}


# Step 1: Filter required columns and drop NAs in dependent variable
regression_data <- new_data %>%
  select(
    CB.Rank..Organization., IPqwery...Patents.Granted,
    IPqwery...Trademarks.Registered, Age, Industries,
    Number.of.Employees.Numeric, Estimated.Revenue.Range.Numeric
  ) %>%
  mutate(CB_Rank = as.numeric(CB.Rank..Organization.)) %>%
  filter(!is.na(CB_Rank)) %>%  
  select(-CB.Rank..Organization.)

# Step 2: Log transform skewed columns
regression_data <- regression_data %>%
  mutate(
    Log_Patents = log1p(IPqwery...Patents.Granted),
    Log_Trademarks = log1p(IPqwery...Trademarks.Registered)
  ) %>%
  select(-IPqwery...Patents.Granted, -IPqwery...Trademarks.Registered)

# Step 3: Split multi-value Industries column into individual categories
# Separate multiple values in the Industries column
regression_data <- regression_data %>%
  mutate(Industries = strsplit(as.character(Industries), ",\\s*")) %>%  # Separate industries by commas
  unnest(Industries) %>%  # Expand the list to multiple lines
  mutate(Industries = trimws(Industries))  

# Step 4: One-hot encoding for Industries column
regression_data <- regression_data %>%
  mutate(Industries = as.factor(Industries)) %>%
  pivot_wider(
    names_from = Industries,
    values_from = Industries,
    values_fn = length,
    values_fill = 0
  )


```

```{r}
View(regression_data)
```


5. standardization 

The necessity of standardization depends on the following points:
Whether the dimensions of the variables are different: For example, the number of patents, the number of trademarks, and age may have different dimensions. If standardization is not performed, some variables will have too much influence on the model.When using linear regression, the variables need to be standardized or normalized.

```{r}

regression_data <- regression_data %>%
  mutate(across(c(Log_Patents, Log_Trademarks, Age, Number.of.Employees.Numeric, Estimated.Revenue.Range.Numeric), scale))

```


```{r}
regression_data <- regression_data %>% drop_na(CB_Rank)

```


# Regression Analysis

Regression Modeling Create a linear regression model to analyze the relationship between CB Rank and the independent variables (patents, trademarks, etc.):
Dependent variable: CB Rank (you can use CB_Rank directly, note that it is a continuous variable, smaller values indicate higher ranking)
Independent variables: Log_Patents, Log_Trademarks, Age, Number.of.Employees.Numeric, Estimated.Revenue.Range.Numeric


```{r}

model <- lm(CB_Rank ~ Log_Patents + Log_Trademarks + Age + Number.of.Employees.Numeric + Estimated.Revenue.Range.Numeric, 
            data = regression_data)


summary(model)

```
Overall model evaluation:

**Multiple R-squared**: 0.0437
Explained 4.37% of the variance in the dependent variable (CB_Rank). This is a very low value, indicating that this model has weak explanatory power for predicting CB_Rank.

**Adjusted R-squared**: 0.01026
The adjusted R² is only 1.03%, which also shows that the model is very limited in predicting CB_Rank.

**F-statistic**: 1.307 (p-value = 0.2643)
The F-test of the model as a whole shows that the p-value is greater than 0.05, indicating that all independent variables together have an insignificant effect on the dependent variable. This may mean that the selected variables cannot explain CB_Rank well, or that the model needs to introduce more important variables.

**Significant variables**:
Number.of.Employees.Numeric is the only significant variable with a coefficient of -77.99, indicating that an increase in the number of employees leads to a lower CB_Rank (higher ranking). This may reflect the fact that larger companies generally have higher market influence and ranking.

**Non-significant variables**:
The p-values of patents (Log_Patents) and trademarks (Log_Trademarks) are both greater than 0.05, indicating that these IP investment indicators have no significant impact on CB_Rank.
Age (Age) and income (Estimated.Revenue.Range.Numeric) also do not significantly affect CB_Rank.

**conclusion** :
Hypothesis H3 was not supported: From the regression analysis, investing in more IP (patents and trademarks) did not show a significant correlation with higher CB_Rank.
Number of employees is the only significant variable: companies with more employees are more likely to have higher market rankings.

Improvement :
Introduce more variables that may be related to CB_Rank, such as the company's industry, region, R&D investment, etc.
Do further exploratory analysis on CB_Rank to consider whether it needs to be grouped or transformed in more detail.

```{r}
View(regression_data)
```


We can continue to try to see if classification regression analysis will have an impact

# Use Logistic Regression for Classification Analysis
We can try to convert CB Rank into a classification variable (such as high, medium, and low rankings) and perform Logistic regression analysis. The steps are as follows:
(1) Convert CB Rank into a categorical variable
```{r}

regression_data <- regression_data %>%
  mutate(CB_Rank_Class = case_when(
    CB_Rank <= 100 ~ "High",
    CB_Rank <= 500 ~ "Medium",
    TRUE ~ "Low"
  )) %>%
  mutate(CB_Rank_Class = factor(CB_Rank_Class, levels = c("High", "Medium", "Low")))


```

(2) Build a multi-classification Logistic Regression model

```{r}

library(nnet)

model <- multinom(CB_Rank_Class ~ Log_Patents + Log_Trademarks + Age + 
                    Number.of.Employees.Numeric + Estimated.Revenue.Range.Numeric +
                    ., data = regression_data)
summary(model)

```

(3) Evaluation model

```{r}

predicted <- predict(model, regression_data)
table(predicted, regression_data$CB_Rank_Class)

```



# Conclusion for H3

### **Evaluation of H3 Hypothesis**
**Hypothesis (H3):** Companies that invest more in IP (have more patents and trademarks) will have a higher CB rank.

1. **Model Summary**  
   - The multinomial logistic regression was conducted to predict CB rank class ("High", "Medium", "Low") using patents, trademarks, age, number of employees, revenue range, and industry variables (one-hot encoded).  
   - The model converged successfully, with a residual deviance close to zero and an AIC of 380.  
   - However, despite the model's statistical fit, certain coefficients (e.g., for patents and trademarks) were not significant, indicating weak evidence to support their direct effect on CB rank class.

2. **Key Findings**  
   - **Patents and Trademarks:**  
     The coefficients for `Log_Patents` and `Log_Trademarks` varied across CB rank classes but were not statistically significant (p > 0.05). This suggests limited evidence to support the hypothesis that IP investment alone strongly correlates with CB rank.  
   - **Other Factors:**  
     Variables like `Number.of.Employees.Numeric` showed some statistical significance in distinguishing rank classes, indicating company size could be more influential than IP investment alone.  

3. **Model Accuracy:**  
   - Based on the confusion matrix, the model classified the CB rank perfectly within the training data (100% accuracy), which could indicate potential overfitting due to the high dimensionality of the industry variables.


### **Limitations**
1. **High Dimensionality:**  
   - The inclusion of numerous industry dummy variables created a high-dimensional feature space, likely leading to multicollinearity and overfitting. This may have reduced the reliability of the coefficients for `Log_Patents` and `Log_Trademarks`.

2. **Class Imbalance:**  
   - If the CB rank classes ("High", "Medium", "Low") are imbalanced in the dataset, the model may favor the majority class, skewing predictions.

3. **Non-linear Relationships:**  
   - Logistic regression assumes linear relationships between predictors and the log odds of the outcome. If the true relationships are non-linear, the model might fail to capture the complexity.

4. **Overfitting:**  
   - Perfect classification within the training data suggests overfitting, limiting the generalizability of the model to new data.

5. **Lack of Interaction Terms:**  
   - Potential interactions between variables (e.g., patents and industry type) were not considered, which might mask the combined effects on CB rank.


## **Future Work**
1. **Feature Selection:**  
   - Use dimensionality reduction techniques, such as LASSO regression, to identify the most impactful predictors and reduce multicollinearity.

2. **Balance the Data:**  
   - Address class imbalance using techniques like SMOTE (Synthetic Minority Oversampling Technique) to improve model robustness.

3. **Explore Non-linear Models:**  
   - Test non-linear models such as decision trees, random forests, or gradient boosting to better capture complex patterns in the data.

4. **Cross-validation:**  
   - Implement k-fold cross-validation to assess the model's performance on unseen data and mitigate overfitting.

5. **Interaction Effects:**  
   - Include interaction terms (e.g., patents × industry) to investigate combined effects on CB rank.

6. **Additional Data:**  
   - Incorporate other potential predictors, such as market share or customer satisfaction, to enhance the explanatory power of the model.

7. **Validation on Test Data:**  
   - Evaluate the model on a separate test dataset to assess generalizability.


### **Conclusion**
While the multinomial logistic regression model provided some insights into the predictors of CB rank, the hypothesis that IP investment strongly influences CB rank was not fully supported by the results. Limitations such as multicollinearity, overfitting, and potential non-linear effects suggest the need for alternative models and additional predictors. Future work should address these limitations to provide a more robust evaluation of the relationship between IP investment and CB rank.





